Flow-Based Cost Allocation in Linear Optimized Power Systems are non-unique but localizable

### 2020-08-26 paper/flow_based.tex
add write table rule
paper, last chapter update install.sh for custom power plants

In order to showcase the cost allocation at a more complex system, we apply it to an cost-optimized German power system model with 50 nodes and one year time span with hourly resolution. The model builds on the PyPSA-EUR workflow \cite{horsch_pypsa-eur_2020} with technical details and assumptions reported in \cite{horsch_pypsa-eur_2018}. We follow a browfield approach where transmission lines can be expanded starting from today's capacity values, originally retreived from the ENTSO-E Transmission System Map \cite{entsoe-e_entso-e_nodate}. Pre-installed generation capacities for wind and solar are distributed proportionally to the average power potential at each site excluding those with an average capacity factor of 10\%. Further, wind and solar capacity expansion are limited by land use restriction. These consider agriculture, urban, forested and protected areas based on the CORINE and NATURA2000 database \cite{corine2012,natura2000}. Pumped Hydro Storages (PHS) are fixed to today's capacities with no more expansion allowed. Additionally, unlimited batteries and H$_{2}$-storages are allowed at each node. We impose a effective carbon price of 120 \euro per tonne-CO$_{2}$.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{de50bf/network}
    \label{fig:network}
    \caption{Brownfield optimization of the German power system. The left side shows existent renewable capacities which serve as lower capacity limits for the optimization. The right side shows the capacity expansion of renewables as well as installation of backup gas power plants. The effective CO$_2$ price is set to 120 \euro per tonne CO$_2$ emission.}
\end{figure*}
The left side of \cref{fig:network} shows the lower capacity bounds for renewable generators and transmission infrastructure, the right side the capacity expansion for generation, storage and transmission. The optimization expands the solar capacity in the south, onshore and offshore wind in the upper north and most west. OCGT generators are build all over the network except for most south and north.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{de50bf/total_costs}
    \label{fig:total_cost}
    \caption{Total allocated payments of the system. }
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{de50bf/average_price}
    \label{fig:average_price}
    \caption{Average electricity price $\lmp$ in the network.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{de50bf/locality_ptpf_net}
    \label{fig:locality}
    \caption{Average distance between payer and receiver for different technologies and shares of the total production.}
\end{figure}

@@

\subsection{Example: Power Flow Allocations of different Types}
\label{sec:example_plots}
\begin{figure}[h!]
    \begin{subfigure}[c]{\linewidth}
    \includegraphics[width=\linewidth]{example_allocation_bus1_net_ebe.png}
    \vspace{-40pt}
    \subcaption{}
    \label{fig:example_allocation_bus1_net_ebe}
    \end{subfigure}
    \begin{subfigure}[c]{\linewidth}
    \includegraphics[width=\linewidth]{example_allocation_bus2_net_ebe.png}
    \vspace{-40pt}
    \subcaption{}
    \label{fig:example_allocation_bus2_net_ebe}
    \end{subfigure}
    \caption{Power allocations for bus~1 (a) and bus~2 (b) of the example network in \cref{fig:example_network} using equivalently allocated net power injections (scheme \ref{net}\ref{ebe}). Bus~1 retrieves 60~MW from itself and nothing from bus~2. The latter in turn retrieves 40~MW from bus~1 and self supplies 50~MW. The P2P trades are less in number and more intuitive then with allocating gross flow.}
    \label{fig:example_allocation_net_ebe}
\end{figure}

>>>>

In order to showcase the cost allocation at a more complex system, we apply it to an cost-optimized German power system model with 50 nodes and one year time span with hourly resolution. The model builds on the PyPSA-EUR workflow \cite{horsch_jonas_pypsa-eur_2020} with technical details and assumptions reported in \cite{horsch_pypsa-eur_2018}. We follow a brownfield approach where transmission lines can be expanded starting from today's capacity values, originally retrieved from the ENTSO-E Transmission System Map \cite{entso-e_entso-e_nodate}. Pre-installed generation capacities totals for wind and solar are distributed in proportion to the average power potential at each site excluding those with an average capacity factor of 10\%. Further, wind and solar capacity expansion are limited by land use restriction. These consider agriculture, urban, forested and protected areas based on the CORINE and NATURA2000 database \cite{corine2012,natura2000}. Pumped Hydro Storages (PHS) are fixed to today's capacities with no more expansion allowed. Additionally, unlimited batteries and H$_{2}$-storages are allowed at each node. We impose a effective carbon price of 120 \euro\, per tonne-CO$_{2}$. All effective cost assumptions on operational costs $o_i$ and annualized capital cost $c_i$ are reported in detail in \cref{sec:cost_assumptions}.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{de50bf/network}
    \caption{Brownfield optimization of the German power system. The left side shows existent renewable capacities which serve as lower capacity limits for the optimization. The right side shows the capacity expansion of renewables as well as installation of backup gas power plants. The effective CO$_2$ price is set to 120 \euro per tonne CO$_2$ emission.}
    \label{fig:network}
\end{figure*}
The resulting network is shown in  \cref{fig:network} with its lower capacity bounds for renewable generators and transmission infrastructure on the left and capacity expansion for generation, storage and transmission on the right. The optimization expands the solar capacity in the south, onshore and offshore wind in the upper north and most west. Open-Cycle Gas Turbines (OCGT) are build within the broad middle of the network. Transmission lines are amplified in along the North-South axis, including one large DC link, leading from the coastal region to the South-West.

\Cref{fig:average_price} displays the average electricity price $\lmp$ per region. We observe a relatively strong gradient from south (at roughly 92 \euro/MWh) to north (80 \euro/MWh).  
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{de50bf/average_price}
    \caption{Average electricity price $\lmp$ in the network.}
    \label{fig:average_price}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{de50bf/total_costs}
    \caption{Total allocated payments of the system. }
    \label{fig:total_cost}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{de50bf/locality_ptpf_net}
    \caption{Average distance between payer and receiver for different technologies and shares of the total production.}
    \label{fig:locality}
\end{figure}

@@

\subsection{Numerical Example: Power Flow Allocation of type \ref{net}\ref{ebe}}
\label{sec:example_plots}
\begin{figure}[h!]
    \begin{subfigure}[c]{\linewidth}
    \includegraphics[width=\linewidth]{example_allocation_bus1_net_ebe.png}
    \vspace{-40pt}
    \subcaption{}
    \label{fig:example_allocation_bus1_net_ebe}
    \end{subfigure}
    \begin{subfigure}[c]{\linewidth}
    \includegraphics[width=\linewidth]{example_allocation_bus2_net_ebe.png}
    \vspace{-40pt}
    \subcaption{}
    \label{fig:example_allocation_bus2_net_ebe}
    \end{subfigure}
    \caption{Power allocations for bus~1 (a) and bus~2 (b) of the example network in \cref{fig:example_network} using equivalently allocated net power injections (scheme \ref{net}\ref{ebe}). Bus~1 retrieves 60~MW from itself and nothing from bus~2. The latter in turn retrieves 40~MW from bus~1 and self supplies 50~MW. The P2P trades are less in number and more intuitive then with allocating gross flow.}
    \label{fig:example_allocation_net_ebe}
\end{figure}

\subsection{Working Example}

\subsubsection{Cost Assumptions}
\label{sec:cost_assumptions}

\begin{table*}
    \centering
    \input{../tables/de50bf_ptpf_net/prices}    
    \caption{Operational and capital price assumptions for all type of assets used in the working example. The capital price for transmission lines are given in [k\,\euro/MW/km]. The cost assumptions are retrieved fromt the PyPSA-EUR model \cite{horsch_jonas_pypsa-eur_2020}.}
\end{table*}
